Markdown to estimate the abundance of brain cell types with the reprocessed counts from MSSM cohorts (with TMM-VOOM normalisation)

### 2017-02-13 code/Rmd/MSSM_RNASeq_Reprocessed_TMM_VOOM_CellProp.Rmd
Temp commit

knit2synapse::knitToFolderEntity(file = "./MSSM_RNASeq_Reprocessed_TMM_VOOM_CellProp.Rmd",
                                 parentId = "syn5570325",
                                 entityName = 'MSSM Cell Type Abundance with Reprocessed RNASeq')
```

@@

```{r synapse.parameters, include=FALSE, cache=TRUE}
# Synapse parameters
parentId = 'syn5570325';
activityName = 'Cell type abundance in MSSM';
activityDescription = 'Cell type abundance in MSSM with TMM-VOOM normalised reprocessed RNASeq counts';

>>>>

knit2synapse::knitToFolderEntity(file = "./MSSM_RNASeq_Reprocessed_TMM_VOOM_CellProp.Rmd",
                                 parentId = "syn5570248",
                                 entityName = 'MSSM Cell Type Abundance with Reprocessed RNASeq')
```

@@

```{r synapse.parameters, include=FALSE, cache=TRUE}
# Synapse parameters
parentId = 'syn5570248';
activityName = 'Cell type abundance in MSSM';
activityDescription = 'Cell type abundance in MSSM with TMM-VOOM normalised reprocessed RNASeq counts';
